\documentclass[format=acmsmall, review=false, screen=true, anonymous=true, table]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{tabularx}
\usepackage{color, colortbl}
\usepackage{tabu}


\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{textcomp}
\usepackage{siunitx}
%\pgfplotsset{compat=1.12}
%\usepackage{pgf-pie}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage[russian,french,english]{babel}
\usepackage{wasysym}
\usepackage{comment}
\usepackage{subfigure}
\usepackage{indentfirst}


\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}


% Metadata Information
\acmJournal{PACMHCI}
\acmVolume{9}
\acmNumber{4}
\acmArticle{39}
\acmYear{2010}
\acmMonth{3}
\copyrightyear{2009}
%\acmArticleSeq{9}

% Copyright
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\acmDOI{0000001.0000001}

% Paper history
\received{February 2007}
\received[revised]{March 2009}
\received[accepted]{June 2009}






\begin{document}
	%
	% paper title
	% can use linebreaks \\ within to get better formatting as desired
%	\title{Towards Bridging the Gap between Multilingual Q\&A Communities with Deep Learning \\
%		\large ---An Empirical Study of Russian Stack Overflow}


%\title[Multi-lingual Stack Overflow]{In Favor of or Against Multi-Lingual Q\&A Sites?: Exploring the Benefits and Concerns of Launching Multi-lingual Q\&A Sites}

\title[Multi-lingual Stack Overflow]{In Favor of or Against Multi-Lingual Q\&A Sites? Exploring the Evidences from User and Knowledge Perspectives}
	
\begin{abstract}
Many Q\&A sites initially run only in English, and then gradually release their multi-lingual variants to serve users who speak other languages.
The launch of such multi-lingual sites always leads to intense dispute about the pros and cons of multi-lingual sites.
Although all arguments and concerns sound reasonable, people can rarely provide solid evidence to convince each other.
In this paper, from users' comments about the launch of several non-English Stack Overflow sites, we first identify three major concerns including community split, knowledge needs and interests in other languages, and knowledge fragmentation and duplication.
To validate these three concerns, we conduct an evidence-based data analysis and comparison of user characteristics, tag usage and cross-site links between the Russian Stack Overflow and the English Stack Overflow on these three concerns.
Our study sheds the light on the existence value and risks of multi-lingual Q\&A sites.

       
\end{abstract}

\begin{comment}
Q\&A sites are emerging as a knowledge sharing and acquisition platform for different users, but most of them run in only one language (mostly English).
As not everyone can ask or answer questions in English, many Q\&A sites now begin to release their multi-lingual variants to serve users who speak other languages.
For example, in addition to the main English Stack Overflow, we now have Russian, Portuguese, Spanish and Japanese Stack Overflow.
The launch of such multi-lingual sites always leads to intense dispute about the pros and cons of multi-lingual sites.
Although all arguments and concerns sound reasonable, people can rarely provide solid evidence of their arguments and concerns to convince each other.
In this paper, from the users' comments about the launch of several non-English Stack Overflow sites, we first identify three major concerns including community split, knowledge needs and interests in other languages, and knowledge fragmentation and duplication.
We then conduct an evidence-based data analysis and comparison of user characteristics, tag usage and cross-site links between the Russian Stack Overflow and the English Stack Overflow on these three concerns.
Our results show that some special knowledge needs and interests in non-English languages warrant the value of multi-lingual Q\&A sites, and multi-lingual Q\&A sites do not result in community split.
However, knowledge fragmentation and duplication across multi-lingual sites is a valid concern.
Although manual cross-site linking can partially deal with this issue, the extent of knowledge fragmentation and duplication calls for automated cross-site linking and cross-site translation support.
%the concerns are not significant and validate the value of multi-lingual variants
\end{comment}

\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10003120.10003130</concept_id>
	<concept_desc>Human-centered computing~Collaborative and social computing</concept_desc>
	<concept_significance>300</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}


%\ccsdesc[500]{Applied computing~Text editing}
\ccsdesc[300]{Human-centered computing~Collaborative and social computing}

%
% End generated code
%


\keywords{Multi-lingual Q\&A Site; Stack Overflow; Community Split; Knowledge Needs and Interests; Knowledge Fragmentation and Duplication; Cross-Lingual Retrieval}

% make the title area
\maketitle
	
	
	% For peer review papers, you can put extra information on the cover
	% page as needed:
	% \ifCLASSOPTIONpeerreview
	% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
	% \fi
	%
	% For peerreview papers, this IEEEtran command inserts a page break and
	% creates the second title. It will be ignored for other modes.
	
	\input{introduction}
	\input{relatedWork}
	\input{motivation}
	\input{empiricalStudy_tag}
	\input{empiricalStudy_user}
	\input{empiricalStudy_link}
	\input{discussion}
	\input{conclusion}
	
	\bibliographystyle{ACM-Reference-Format}
    \bibliography{reference}	

	
	% that's all folks
\end{document}


